\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-14 analytics/dsl.tex
Tech
Small fixes

The \textbf{complexity} of a search query is the number of fields that aren't course number or department that it spans (the accepted fields are shown in Table \ref{fig:sc-fields}).

@@

  \end{tabular}
  \vspace{10pt}
  \caption{``Complex'' search fields (omits only number and department)}
  \label{fig:sc-fields}
\end{table}
\end{center}
\doublespacing

@@

It is possible that user have neither, both, or only a \emph{first increase} metric.

@@

    \#1
    & ``{\tt CSC}''
    & \rightarrow
    & 0
    & 
    \\

    \#2
    & ``{\tt MTH 165}''
    & \rightarrow
    & 0
    & 
    \\

@@

  Other possibilities include linking the credits field of each course to a credits search, the CRN field of a section to a CRN search, the ``{\tt W}'' part of the course code to an upper-level writing search, having a crosslisted course link search the crosslisting of the two departments (instead of directly link to the crosslisted course), a ``feeling lucky?'' button for a search with ``{\tt random}''.}
\end{enumerate}

@@

The amount of users whose first searches are of nonzero complexity may be surprising. The vast majority of these are \textbf{title} searches however, which \emph{are} included in the ``complex'' field table. This is purposeful---title searches only represent 8\% of all search field uses, as we saw in Figure \ref{fig:searchtypes} of the section before last. Moreover, a user's understanding and/or intuition that the Skedge search field is free-form and can be used for different search fields simultaneously is already a significant conceptualization of SkedgeQL, albeit a relatively basic field.

@@

  \caption{Users with a schedule and more than one search split by their number of increases in search complexity}
  \label{fig:sc-pie}
\end{figure}

>>>>

The \textbf{complexity} of a search query is the number of fields that aren't \emph{course number} or \emph{department} that it spans. The accepted fields are shown in the following table:

@@

  \end{tabular}
  \vspace{10pt}
  \caption{``Complex'' search fields (omits only \emph{number} and \emph{department})}
  \label{fig:sc-fields}
\end{table}
\end{center}
\doublespacing

@@

It is possible that a user has neither metric, both metrics, or only a \emph{first increase} metric.

@@

    \#1
    & ``{\tt CSC}''
    & \rightarrow
    & 0
    & \hspace{55pt} ---
    \\

    \#2
    & ``{\tt MTH 165}''
    & \rightarrow
    & 0
    & \hspace{55pt} ---
    \\

@@

  Other possibilities include linking the credits field of each course to a credits search, the CRN field of a section to a CRN search, the ``{\tt W}'' part of the course code to an upper-level writing search, having a crosslisted course link search the crosslisting of the two departments (instead of directly link to the crosslisted course), or a ``feeling lucky?'' button for a search with ``{\tt random}''.}
\end{enumerate}

@@

The amount of users whose first searches are of nonzero complexity may be surprising. The vast majority of these are \textbf{title} searches however, which \emph{are} included in the ``complex'' field table. This is purposeful---title searches only represent 8\% of all search field uses, as we saw in Figure \ref{fig:searchtypes} of the section before last. Moreover, a user's understanding and/or intuition that the Skedge search field is free-form and can be used for different search fields simultaneously is already a significant conceptualization of SkedgeQL, albeit for a relatively basic search type.

@@

  \caption[Users split by their number of increases in search complexity]{Users with a schedule and more than one search split by their number of increases in search complexity}
  \label{fig:sc-pie}
\end{figure}

### 2016-04-14 analytics/npa.tex
Small fixes

  As expected, and unlike the results of further direct-search analysis, the sections added/bookmarked when browsing within 0 navigations were mostly \emph{main} sections (only 37\% of them were subsections). This makes sense, as users may not be concerned with subsections if the goal of the browse is merely to mark interesting courses. This criterion saw more drastic drops in subsection amounts as well, as the number of navigationss increased: 5\% subsections for ${navs}=1$, and 4\% subsections for ${navs}=2$.

>>>>

  As expected, and unlike the results of further direct-search analysis, the sections added/bookmarked when browsing within 0 navigations were mostly \emph{main} sections (only 37\% of them were subsections). This makes sense, as users may not be concerned with subsections if the goal of the browse is merely to mark interesting courses. This criterion saw more drastic drops in subsection amounts as well, as the number of navigations increased: 5\% subsections for ${navs}=1$, and 4\% subsections for ${navs}=2$.

### 2016-04-14 design/search.tex
Small fixes

  Elective courses can either be courses that are required for a major or minor, but are chosen by the student, or they can be courses of particular interest to students who have the flexibility to take them,. For this use-case, Skedge offers search, filter, and sorting features that substantially aid users in browsing through courses and discovering ones they might want to take. Note that none of the following features are supported by CDCS.

@@

    \item SkedgeQL includes the ``new'' keyword, which qualifies an accompanying search by only displaying the courses that were not offered the previous year for that term. For instance, searching ``new csc'' today (Fall 2016) would show Fall Computer Science courses that have been added to the catalog or changed since Fall 2015.
    \item SkedgeQL could include an ``autofit'' keyword, which would take into account the user's current schedule, and only show sections that would not conflict with any already scheduled times.\footnote{This feature is under development and is not currently live.}
    \item SkedgeQL includes the ``random'' keyword, which displays a single random course matching the accompanying query. For instance, ``random csc'' would show a random course in Computer Science for the current term. Used in conjunction with ``autofit'', it can a powerful way to find interesting new classes that are available for users to try.
    \item SkedgeQL includes sorting by class size---useful for students trying to find smaller, discussion based classes---or by class starting time---for students with preferences of morning or afternoon/evening classes.
    \item Instructor names appearing in courses automatically link to searches for more courses taught by that instructor, which is easier than having to use the CDCS ``instructor'' field to make a separate search.

>>>>

  Elective courses can either be courses that are required for a major or minor, but are chosen by the student, or they can be courses of particular interest to students who have the flexibility to take them. For this use-case, Skedge offers search, filter, and sorting features that substantially aid users in browsing through courses and discovering ones they might want to take. Note that none of the following features are supported by CDCS.

@@

    \item SkedgeQL includes the ``{\tt new}'' keyword, which qualifies an accompanying search by only displaying the courses that were not offered the previous year for that term. For instance, searching ``{\tt new csc}'' today (Fall 2016) would show Fall Computer Science courses that have been added to the catalog or changed since Fall 2015.
    \item SkedgeQL could include an ``{\tt autofit}'' keyword, which would take into account the user's current schedule, and only show sections that would not conflict with any already scheduled times.\footnote{This feature is under development and is not currently live.}
    \item SkedgeQL includes the ``{\tt random}'' keyword, which displays a single random course matching the accompanying query. For instance, ``{\tt random csc}'' would show a random course in Computer Science for the current term. Used in conjunction with ``{\tt autofit}'', it can a powerful way to find interesting new classes that are available for users to try.
    \item SkedgeQL includes sorting by class size---useful for students trying to find smaller, discussion based classes---or by class starting time---for students with preferences of morning or afternoon/evening classes.
    \item Instructor names appearing in courses automatically link to searches for more courses taught by that instructor, which is easier than having to use the CDCS ``instructor'' field to make a separate search.

### 2016-04-14 tech.tex
Small fixes

Course \emph{likes} are also entirely locally stored and have nothing to do with Facbeook---Skedge merely uses the same concept and a similar icon for its own feature. Comments on courses are not currently supported, although Facebook-integrated comments would be possible.

@@

As the saying goes, ``if it's not monitored, it's not in production'' (how else would we know that it's truly live?) \cite{monitored}.

>>>>

Course \emph{likes} are also entirely locally stored and have nothing to do with Facebook---Skedge merely uses the same concept and a similar icon for its own feature. Comments on courses are not currently supported, although Facebook-integrated comments would be possible.

@@

As the saying goes, ``if it's not monitored, it's not in production'' (how else would we know if it's really live?) \cite{monitored}.
